Place of death in NRS COVID-19 deaths

### 2021-02-15 covid_nrs_place_of_death.Rmd
modified script to create an outputs folder based on the latest data everytime its run so hat rerunning the script weekly will produce new figures;
also made small modifications to map-based plots

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_annual_deaths_by_age_group_2020",.x), plot = figure_annual_deaths_by_age_group_2020, width = 12, height = 7, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_place_of_death",.x), plot = figure_place_of_death, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home",.x), plot = figure_deaths_at_home, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_2020",.x), plot = figure_deaths_at_home_2020, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_by_health_board",.x), plot = figure_deaths_at_home_by_health_board, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_2week_average_by_health_board",.x), plot = figure_deaths_at_home_2week_average_by_health_board, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_by_local_authority",.x), plot = figure_deaths_at_home_by_local_authority, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_2week_average_by_local_authority",.x), plot = figure_deaths_at_home_2week_average_by_local_authority, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_by_age",.x), plot = figure_deaths_at_home_by_age, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_deaths_at_home_by_sex",.x), plot = figure_deaths_at_home_by_sex, width = 12, height = 9, dpi = 300)
)

@@

## Ratio of 2020 home deaths to historical home deaths by LA

@@

minimum_ratio_between_hb_and_la_home_deaths <-
  bind_rows(
    total_deaths_la,
    total_deaths_hb
  ) %>%
  filter(year==2020 & place_of_death == "Home & other non-institution") %>%
  .$ratio_annual_deaths_to_historical_mean %>%
  min %>%
  round(digits=1)

# TODO: work out the size of these plots

figure_map_ratio_home_deaths_2020_to_historical_la <-
  total_deaths_la %>%
  filter(
    year == 2020 & place_of_death == "Home & other non-institution"
  ) %>%
  left_join(shapefile_la, by=c("ref_area"="LAD20NM")) %>%
  ggplot(aes(geometry=geometry, fill=ratio_annual_deaths_to_historical_mean), colour="grey10") +
  geom_sf(colour="grey10") +
  scale_fill_viridis_b(limits = c(minimum_ratio_between_hb_and_la_home_deaths, maximum_ratio_between_hb_and_la_home_deaths)) +
  theme_minimal() +
  theme(axis.text = element_blank()) +
  labs(x="", y="",
       subtitle = "Ratio of home deaths in 2020 to historical mean 2015-2019, by Local Authority",
       caption = paste0(c(areas_relatively_higher_number_home_deaths, home_deaths_ratio, source_nrs_text), collapse="\n"),
       fill = "Ratio"
       ) +
  NULL

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_map_ratio_home_deaths_2020_to_historical_la",.x), plot = figure_map_ratio_home_deaths_2020_to_historical_la, width = 12, height = 15, dpi = 300)
)

figure_map_ratio_home_deaths_2020_to_historical_hb <-
  total_deaths_hb %>%
  filter(
    year == 2020 & place_of_death == "Home & other non-institution"
  ) %>%
  left_join(shapefile_hb_uk_wide, by=c("ref_area"="name")) %>%
  ggplot(aes(geometry=geometry, fill=ratio_annual_deaths_to_historical_mean), colour="grey10") +
  geom_sf(colour="grey10") +
  scale_fill_viridis_b(limits = c(minimum_ratio_between_hb_and_la_home_deaths, maximum_ratio_between_hb_and_la_home_deaths)) +
  theme_minimal() +
  theme(axis.text = element_blank(), aspect.ratio = 1.4) +
  labs(x="", y="",
       subtitle = "Ratio of home deaths in 2020 to historical mean 2015-2019, by Health Board",
       caption = paste0(c(areas_relatively_higher_number_home_deaths, home_deaths_ratio, source_nrs_text), collapse="\n"),
       fill = "Ratio"
       ) +
  NULL

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0("./outputs/figure_map_ratio_home_deaths_2020_to_historical_hb",.x), plot = figure_map_ratio_home_deaths_2020_to_historical_hb, width = 12, height = 15, dpi = 300)
)

```

>>>>

## Set up output directory

Because data are updated on a weekly basis, we'll have a separate directory for every week the data are updated:

```{r}
latest_data_date <- strftime(max(table_of_data_sources$last_modified), format="%F")

dir_outputs <- paste0("./outputs/",latest_data_date)
if (!dir.exists(dir_outputs)) dir.create(dir_outputs)
```

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_annual_deaths_by_age_group_2020",.x), plot = figure_annual_deaths_by_age_group_2020, width = 12, height = 7, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_place_of_death",.x), plot = figure_place_of_death, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home",.x), plot = figure_deaths_at_home, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_2020",.x), plot = figure_deaths_at_home_2020, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_by_health_board",.x), plot = figure_deaths_at_home_by_health_board, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_2week_average_by_health_board",.x), plot = figure_deaths_at_home_2week_average_by_health_board, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_by_local_authority",.x), plot = figure_deaths_at_home_by_local_authority, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_2week_average_by_local_authority",.x), plot = figure_deaths_at_home_2week_average_by_local_authority, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_by_age",.x), plot = figure_deaths_at_home_by_age, width = 12, height = 9, dpi = 300)
)

@@

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_deaths_at_home_by_sex",.x), plot = figure_deaths_at_home_by_sex, width = 12, height = 9, dpi = 300)
)

@@

## Ratio of 2020 home deaths to historical home deaths by LA / HB

@@

minimum_ratio_between_hb_and_la_home_deaths <-
  bind_rows(
    total_deaths_la,
    total_deaths_hb
  ) %>%
  filter(year==2020 & place_of_death == "Home & other non-institution") %>%
  .$ratio_annual_deaths_to_historical_mean %>%
  min %>%
  round(digits=1)
```

### LA

```{r, fig.height=12, fig.width=8}
# TODO: work out the size of these plots
figure_map_ratio_home_deaths_2020_to_historical_la <-
  total_deaths_la %>%
  filter(
    year == 2020 & place_of_death == "Home & other non-institution"
  ) %>%
  left_join(shapefile_la, by=c("ref_area"="LAD20NM")) %>%
  ggplot(aes(geometry=geometry, fill=ratio_annual_deaths_to_historical_mean), colour="grey10") +
  geom_sf(colour="grey10") +
  scale_fill_viridis_b(limits = c(minimum_ratio_between_hb_and_la_home_deaths, maximum_ratio_between_hb_and_la_home_deaths)) +
  theme_minimal() +
  theme(axis.text = element_blank()) +
  labs(x="", y="",
       title = "Ratio of home deaths in 2020 to historical mean 2015-2019, by Local Authority",
       subtitle = "A ratio of 1 means there was no increase; A ratio of 1.6 means there was a 60% increase of home deaths in 2020 over the mean 2015-2019.",
       caption = paste0(c(areas_relatively_higher_number_home_deaths, home_deaths_ratio, source_nrs_text), collapse="\n"),
       fill = "Ratio"
       ) +
  NULL

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_map_ratio_home_deaths_2020_to_historical_la",.x), plot = figure_map_ratio_home_deaths_2020_to_historical_la, width = 9, height = 12, dpi = 300)
)

figure_map_ratio_home_deaths_2020_to_historical_la
```

### HB

```{r, fig.height=12, fig.width=8}
# TODO: work out the size of these plots
figure_map_ratio_home_deaths_2020_to_historical_hb <-
  total_deaths_hb %>%
  filter(
    year == 2020 & place_of_death == "Home & other non-institution"
  ) %>%
  left_join(shapefile_hb_uk_wide, by=c("ref_area"="name")) %>%
  ggplot(aes(geometry=geometry, fill=ratio_annual_deaths_to_historical_mean), colour="grey10") +
  geom_sf(colour="grey10") +
  scale_fill_viridis_b(limits = c(minimum_ratio_between_hb_and_la_home_deaths, maximum_ratio_between_hb_and_la_home_deaths)) +
  theme_minimal() +
  theme(axis.text = element_blank(), aspect.ratio = 1.4) +
  labs(x="", y="",
       title = "Ratio of home deaths in 2020 to historical mean 2015-2019, by Health Board",
       subtitle = "A ratio of 1 means there was no increase; A ratio of 1.6 means there was a 60% increase of home deaths in 2020 over the mean 2015-2019.",
       caption = paste0(c(areas_relatively_higher_number_home_deaths, home_deaths_ratio, source_nrs_text), collapse="\n"),
       fill = "Ratio"
       ) +
  NULL

walk(
  .x = c(".pdf",".svg",".png"),
  .f = ~ggsave(filename = paste0(dir_outputs,"/figure_map_ratio_home_deaths_2020_to_historical_hb",.x), plot = figure_map_ratio_home_deaths_2020_to_historical_hb, width = 9, height = 12, dpi = 300)
)

figure_map_ratio_home_deaths_2020_to_historical_hb
```
